\documentclass[12pt]{article}

%% Define some new colors
\usepackage{xcolor}
\definecolor{mBlue}{RGB}{51, 77, 167}
\newcommand{\blue}[1]{{\color{mBlue}#1}}

%% Page and text formatting
\usepackage[left=1.0in, right=1.0in, top=1.0in, bottom=1.0in]{geometry} % margins
\usepackage{setspace}
\singlespacing % No more than 6 lines of text per inch
\usepackage{amsmath, amsfonts}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{lastpage}

%% Make the sections start with (a), (b), etc.
\renewcommand\thesection{(\alph{section})}
\renewcommand\thesubsection{(\alph{subsection})}

%% Set up footer
\usepackage{fancyhdr}
\fancypagestyle{CVfooter}
{
 \lhead{}
 \chead{}
 \rhead{}
 \lfoot{\small{Jorge J.\ Ortiz}}
 \cfoot{\small{\today}}
 \rfoot{\small{\thepage/\pageref{LastPage}}}
 \renewcommand{\headrulewidth}{0.0pt}
 \renewcommand{\footrulewidth}{0.5pt}
}

%% Set up hyperlinks
\usepackage[linktoc=page]{hyperref}
\hypersetup{
  colorlinks = true,
  urlcolor = mBlue,
  citecolor = mBlue,
  linkcolor = mBlue,
}

%% Set up citations and bibliography
\usepackage{bibunits}
\usepackage[sort&compress,super]{natbib}
\defaultbibliographystyle{apsrev4-2}
\setcitestyle{comma}
\setlength{\bibsep}{0pt}
\renewcommand{\bibnumfmt}[1]{\ \ \ #1.}
\renewcommand\refname{\vspace{-7mm}}

%% This allows us to start a bibliography with arbitrary number
\usepackage{etoolbox}
\makeatletter
\newcommand*{\newbibstartnumber}[1]{%
  \apptocmd{\thebibliography}{%
    \global\c@NAT@ctr #1\relax
    \addtocounter{NAT@ctr}{-1}%
  }{}{}%
}
\makeatother

%% Reduce whitespace around lists (globally)
\usepackage{enumitem}
\setlist[itemize]{nosep,left=0pt}
\setlist[enumerate]{nosep}
\setlist[description]{nosep}

%% Formatting for sections
\usepackage[compact]{titlesec}
\titleformat*{\section}{\normalsize\bfseries}
\titlespacing*{\section}{0mm}{2mm}{1mm}[0mm] % left top bottom right
\titleformat*{\subsection}{\normalsize\bfseries}
\titlespacing*{\subsection}{0mm}{2mm}{1mm}[0mm]
\titleformat*{\subsubsection}{\normalsize\bfseries\itshape}
\titlespacing*{\subsubsection}{0mm}{1mm}{0mm}[0mm]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[left=2.5cm,right=2.5cm,top=1.5cm,bottom=2.5cm]{geometry}
\usepackage{enumitem}


% as bibentry and hyperref clash in some cases, this is a workaround
% as suggested by the following two links:
%https://tex.stackexchange.com/questions/227933/using-bibentry-to-cite-in-text-reference-with-apacite
% and
%https://tex.stackexchange.com/questions/65348/clash-between-bibentry-and-hyperref-with-bibstyle-elsart-harv/65401#65401
\usepackage{bibentry}
\makeatletter\let\saved@bibitem\@bibitem\makeatother
\usepackage[colorlinks=true]{hyperref}
\makeatletter\let\@bibitem\saved@bibitem\makeatother


% hanging publications: 1st line starts at beginning of line, 
% further lines are placed a bit to the right
\usepackage{hanging}
\newcommand\publication[1]{%
	\smallskip\par\hangpara{1.5em}{1}\bibentry{#1}\smallskip
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%








\begin{document}
\pagestyle{CVfooter}

\noindent \textbf{\uppercase{curriculum vitae}}
\vspace{2mm}

\noindent \textbf{Jorge J.\ Ortiz}
\vspace{1mm}

\noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}
Assistant Professor\\ Electrical and Computer Engineering & Email: \href{mailto:jortiz@alum.mit.edu}{jortiz@alum.mit.edu} \\
Rutgers University & Web: \href{http://jorgeortizphd.info}{http://jorgeortizphd.info} \\
94 Brett Road, & Phone: 617-784-6550 \\
Piscataway, NJ 08854-8058 &  \\
\hline
\end{tabular*}

\section{Education \& Training}

\begin{tabular}{l l l l}
University of California & Berkeley, CA & Computer Science & Ph.D., 2013 \\
University of California & Berkeley, CA & Computer Science & M.S., 2010 \\
M.I.T. & Cambridge, MA & Computer Science & B.S., 2003 \\
\end{tabular}

\section{Academic Appointments}

\begin{tabular}{l l}
Sept. 2018 -- present & Assistant Professor, Rutgers University \\
\end{tabular}

\section{Industry Experience}

\begin{tabular}{l l}
Dec. 2019 -- present & Quant. Research Baseball Ops., New York Yankees \\
Dec. 2013 -- Aug. 2018 & Research Staff Member, IBM Research \\
Jan. 2013 -- Sept. 2013 & Senior Software Engineer, Spire Global \\
Aug. 2003 -- Feb. 2007 & Software Engineer, Oracle Corp. \\
\end{tabular}

\section{Honors and Invited Talks}
\begin{itemize}
    \item Invited speaker at Columbia University, Embedded AI Seminar, February 2022
    \item Invited speaker at Texas Tech University (TTU) Computer Science Colloquium, February 2022
    \item Invited speaker at New Jersey Institute of Technology (NJIT) Computer Science Colloquium, November 2021
    \item Invited speaker at University of Massachusetts at Amherst (UMass Amherst) ECE Colloquium, October 2020
    \item Invited speaker at University of Southern California (USC), CPS-IoT Webinar, October 2020
    \item Invited speaker at NSF Workshop on the Dynamic Interaction of Embodied Human and Machine Intelligence, May 2019
    \item Invited speaker ECE Seminar at Emory University, February 2019
    \item {\bf Keynote Speaker}: Workshop on Smart and Connected Indoor Environments \emph{in conjunction with IEEE International Conference on Sensing, Communication and Networking (SECON 2017)}
    \item Qualcomm Innovation Fellowship Finalist 2011
    \item NSF Graduate Fellowship Honorable Mention 2008
    \item Ford Foundation Diversity Fellowship Honorable Mention 2008
\end{itemize}

\section{Grants and Funding}
\begin{itemize}
    \item NSF Engineering Research Center: The Center for Smart Streetscapes, National Science Foundation Award Abstract \#2133516. Site PI Jorge Ortiz. \$26,000,000 (\$2.3M Rutgers portion).
    \item IUCRC Planning Grant Rutgers University: Center for Standards and Ethics in Artificial Intelligence (CSEAI), National Science Foundation Award Abstract \#2137245.  PI Jorge Ortiz. \$20,000.%\href{link}{https://www.nsf.gov/awardsearch/showAward?AWD_ID=2137245&HistoricalAwards=false}
    \item Social Intelligence in the Automobile, Nissan Corporation. PI Jorge Ortiz. \$20,000.
    \item ASPECT: Active Learning to Understand Family Social Behaviors in Automobile, Nissan Corporation. \$20,000.
    \item SII Planning: ARIES: Center for Agile, RelIablE, Scalable Spectrum, National Science Foundation . PI: Narayan Mandayam. Co-PI Jorge Ortiz (25\% effort). \$50,000.
    
    % \item NRT-AI: AI-Enabled Learning Factory for Advanced Manufacturing (AI-iAM), National Science Foundation. PI Yuebin Guo, Co-PI Jorge Ortiz (33\% effort). \$3,000,000.  \textbf{Finalist, pending.} 
\end{itemize}

\section{Ph.D. Students}
\begin{itemize}
    \item Tahiya Chowdhury. Data-driven Techniques For Human Activity Sensing In Smart Environments.  Expected graduation 12/2022.
    \item Murtadha Aldeer. Techniques and Systems for Smart Medication Adherence. Co-advisor: Richard Martin. Expected graduation 12/2022.
    \item Tong Wu.  Human-Centered Machine Learning for Smart Sensing in Vehicles. Expected graduation 05/2023.
    \item Yuan Sun. Social Intelligence and Interaction in Sensed Environments. Expected graduations 05/2025.
\end{itemize}


\section{Recent Publications}
\input{pubs}

\newpage
\section{Service}
\begin{enumerate}
    \item General Chair Buildsys 2022
    \item Chair for Workshop on Cyber-Physical-Human Systems (CPHS) at CPS Week 2022
    \item NeurIPS 2021 Workshop on The Symbiosis of Deep Learning and Differential Equations (DLDE), Organizer
    \item AAAI-22 Undergraduate Consortium -- Mentorship Coordinator Chair
    \item TPC The First International Workshop on Cyber-Physical-Human System Design and Implementation at CPS Week 2021
    \item EWSN 2021 Poster Co-Chair
    \item Buildsys 2020 TPC Co-Chair, Steering Committee 2021, TPC 2021, Poster Chair 2021
    \item AAAI-21 Undergraduate Consortium -- Faculty Mentor
    \item AAAI-20 Undergraduate Consortium -- Faculty Mentor
    \item LatinX in AI Mentor 2020
    % \item New York Scientific Data Summit (NYSDS) 2020 Co-Chair
    \item Co-Chair N2Women at Sensys 2019
    \item Co-Chair Workshop on Combining Physical and Data-Driven Knowledge in Ubiquitous Computing at UBICOMP 2019
    \item CPS-IoT Week 2019 Publication Chair (HSCC, ICCPS, IPSN, RTAS, IoTDI)
    \item Richard Tapia Celebration in Diversity in Computing Poster Co-Chair 2018, Chair 2019
    \item TPC Member Latinos in Artificial Intelligence Workshop NeurIPS 2018, ICML 2019
    \item TPC Member Energy Data and Analytics Workshop at e-Energy 2018, 2019
    \item TPC Member Sensys 2016 (Demo Session), Organizing Committee 2020
    \item TPC Member IPSN 2014, 2017, 2019, 2020, 2021
    \item TPC Member Buildsys 2016, 2017, 2018, 2019, 2020
    \item Organizing Committee Sensys/Buildsys 2016, 2017, 2020
    \item The 26th International Conference on Computer Communication and Networks (ICCCN 2017)
    \item TPC Member 1st Workshop on Smart and Connected Indoor Environments (SCIE) in conjunction with IEEE International Conference on Sensing, Communication and Networking (SECON 2017)
    \item TPC Member 1st Workshop on Internet of Thing Physical Data Analytics (IoTPDA) in conjunction with IEEE International Conference on Sensing, Communication and Networking (SECON 2016)
    \item TPC Member DCOSS 2016 (The annual International Conference on
    Distributed Computing in Sensor Systems)
    \item TPC Member ALGOSENSORS 2017 
    \item TPC IEEE workshop on Big Data Management for the Internet of Things (BIOT2017)
    \item Member of CSGSA Faculty Candidate Evaluation Committee, UCB Computer Science Div. (2008, 2009, 2010)
    \item President of CSGSA Faculty Candidate Evaluation Committee, UCB Computer Science Div. (2011)
    \item Chair, Internet of Things Professional Interest Community (IoT-PIC) IBM Research at Watson Labs.
\end{enumerate}



\end{document}

